---
title: "2023 HI ARA Analysis"
author: "Angel Avalos"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
---

# 2023 HI ARA Analysis

### Import packages and set working directory.

##### R
```{r setup, warning=FALSE, message=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(reticulate)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
```

##### Python
``` {python setup_2, message=FALSE}
import pandas as pd
import numpy as np
import os
from sklearn import linear_model
```

##### ARA Data
``` {python import, eval=FALSE}
# Importing file
data = pd.read_csv("data/ara-reports.csv")
data = data.replace(r'^\s*$', np.nan, regex=True)
data = data.rename(columns={"Date":"total-date"})
# Extracting date
for i,v in enumerate(data["total-date"]):
  if type(v) == str:
    name = v[:-12]
    data.at[i,"total-date"] = name
  
data["date"] = pd.to_datetime(data["total-date"])
data = data.sort_values("date")

data.to_csv("output/ara-report-dates.csv",index=False)
```

### 2023 ARAs

##### Extract Ethylene Peaks for samples. Convert to nmol ethylene/hr/OD.
```{python ara-data}
toptop=pd.DataFrame()
for i in os.listdir("data/"):
  if os.path.isdir("data/"+i):
    path = "data/"+i
    top = pd.DataFrame()
    for j in os.listdir(path):
      name = j.split("_",1)[1].replace("_rep1_MS.csv","").replace("_rep2_MS.csv","").replace("_rep3_MS.csv","").replace("_rep4_MS.csv","").replace("_MS_1.csv","").replace("_rep5_MS.csv","").replace("_MS.csv","")
      # At later dates, I stopped running neg for samples so I didn't say they were "pos". Need to add that label.
      if "pos" not in name and "neg" not in name:
        name = name+"_pos"
      data = pd.read_csv(path+"/"+j, header=3)
      data = data.iloc[:,1:24]
      # Note that these criteria are based on manual inspection of values, subject to change.
      data = data[data["RT"].between(2.4,2.68)]
      # Some small peaks of non-ethylene mess with getting ethylene peak only.
      # If ethylene is present, it is the highest peak, so getting the highest peak within the RT range.
      data = data[data["Area"]==data["Area"].max()]
      data.insert(loc=0,column="ID",value=name)
      top = pd.concat([top,data], axis=0)
    # Blanking, and remove blanks from final dataframe.
    if "uninoc_pos" in top["ID"].to_list():
      blank = top[top["ID"]=="uninoc_pos"]["Area"].mean()
      top = top[top["ID"]!="uninoc_pos"]
      top["Area"] = top["Area"]-blank
      top.reset_index(drop=True,inplace=True)
      top.insert(loc=24,column="date",value=i)
      toptop = pd.concat([top,toptop], axis=0)
    else:
      blank = top[top["ID"]=="blank_pos"]["Area"].mean()
      top = top[top["ID"]!="blank_pos"]
      top["Area"] = top["Area"]-blank
      top.reset_index(drop=True,inplace=True)
      top.insert(loc=24,column="date",value=i)
      toptop = pd.concat([top,toptop], axis=0)
toptop.reset_index(drop=True,inplace=True)
# "Pos" samples have acetylene. "Neg" do not. Separate.
#pos = toptop[toptop["ID"].str.contains("pos")]
#neg = toptop[toptop["ID"].str.contains("neg")]

# Convert peak area to nmol ethylene.
toptopnmol=pd.DataFrame()
# Run for loop for dates in order so if no std curve for that date
# then use the most recent std curve before that date.
toptop["date"]=pd.to_numeric(toptop["date"])
dates=[i for i in toptop["date"].unique()]
dates.sort()
for i in dates:
  subs=toptop[toptop["date"]==i]
  # This uses an old std curve calculation.
  if i<20231208:
    subs["nmol-eth"]=(subs["Area"]-17690)/383.46
    subs["nmol-eth/hr/OD"]=(subs["nmol-eth"]/48/0.1)
    toptopnmol=pd.concat([subs,toptopnmol],axis=0)
  # This uses the std curve run on the same day.
  elif subs["ID"].str.contains("ppm").any():
    subsppm=subs[subs["ID"].str.contains("ppm")]
    #subsppm=subsppm[~subsppm["ID"].str.contains("_N_")]
    if subsppm["ID"].str.contains("_N_").any():
      subsppm["concentration"]=pd.to_numeric(subsppm["ID"].str.replace("ppm_N_pos",""))
    else:
      subsppm["concentration"]=pd.to_numeric(subsppm["ID"].str.replace("ppm_pos",""))
    # At STP, there are 669245.5nmol gas in 15mL of headspace. This is what we're assuming.
    # To convert ppm to nmol of gas, simply take the proportion of the nmol total.
    subsppm["nmol"]= 669245.5*(subsppm["concentration"]/1E6)
    x=subsppm["nmol"].values
    y=subsppm["Area"].values
    x=x.reshape(len(x),1)
    y=y.reshape(len(x),1)
    regr=linear_model.LinearRegression().fit(x,y)
    coef=regr.coef_[0]
    intercept=regr.intercept_[0]
    subs["nmol-eth"]=(subs["Area"]-intercept)/coef
    subs["nmol-eth/hr/OD"]=(subs["nmol-eth"]/48/0.1)
    toptopnmol=pd.concat([subs,toptopnmol],axis=0)
  else:
    # Since this is run sequentially by date, just use the last values if don't have ppm.
    subs["nmol-eth"]=(subs["Area"]-intercept)/coef
    subs["nmol-eth/hr/OD"]=(subs["nmol-eth"]/48/0.1)
    toptopnmol=pd.concat([subs,toptopnmol],axis=0)
# Remove std curve samples.
toptopnmol=toptopnmol[~toptopnmol["ID"].str.contains("ppm")]
# Remove blank samples.
toptopnmol=toptopnmol[~toptopnmol["ID"].str.contains("blank")]
# Remove samples without acetylene.
toptopnmol=toptopnmol[~toptopnmol["ID"].str.contains("neg")]
# Remove empty samples.
toptopnmol=toptopnmol[~toptopnmol["ID"].str.contains("empty")]
toptopnmol["date"]=toptopnmol["date"].astype(str)
toptopnmol["new-ID"]=toptopnmol["ID"].str.replace("_pos","_")+toptopnmol["date"]

#Subsetting for samples run with both old and new septa.
multilist=[i for i in toptopnmol["ID"] if len(toptopnmol[toptopnmol["ID"]==i])>3]
multi=toptopnmol[toptopnmol["ID"].isin(multilist)]
multi.reset_index(drop=True,inplace=True)

# We're assuming 48hr incubation for all. There are slight variations (+-2hr). Can correct in the future.

# Removing Totontepec.
#meta=pd.read_csv("data/2022-06-30_molokai-isolate-catalog - Copy.csv")
#meta=meta.iloc[:-1,:]
#toton=meta[meta["Sample Type "].str.contains("Totontepec")]
#len(toton)
#toton["BCW_ID"]=toton["BCW_ID"].str.replace("BCW_","BCW")
#non = list(set([i for i in pos["ID"] if i.replace("_pos","") not in toton["BCW_ID"].to_list()]))
#nontoton=pos[pos["ID"].isin(non)]
#final_non=pd.DataFrame({"ID":nontoton["ID"].str.replace("_pos","").unique()})
#final_non.to_csv("../2023_wgs_dna/data/20231106_nontoton-ara-screened.csv",index=False)
#len(pos["ID"].unique())

```

##### Plot nmol ethylene/hr/od. Bar charts.
```{r plot, fig.width=10}
data = py$toptopnmol
data$date=as.numeric(data$date)
multi=py$multi
multi$date=as.numeric(multi$date)

# Ethylene bar chart, ordered by magnitude.
ggplot(data=data, aes(x=reorder(`new-ID`,-`nmol-eth/hr/OD`), y=`nmol-eth/hr/OD`)) +
  geom_bar(stat="summary",fun="mean", aes(fill=as.factor(date))) + 
  geom_point() +
  geom_hline(yintercept=750,linetype="dashed")+
  scale_y_continuous(breaks=c(0,500,750,1000,1500,2000,2500),labels=c(0,500,"A. brasilense",1000,1500,2000,2500)) +
  #annotate("text",x=100,y=750,label="A. brasilense (Van Deynze et. al 2018)") +
  ylab("Nanomoles of Ethylene/hr/OD600") +
  xlab("Isolate") +
  theme(axis.text.x = element_blank())

# Ethylene bar chart, ordered by date.
ggplot(data=data, aes(x=reorder(`new-ID`,`date`), y=`nmol-eth/hr/OD`)) +
  geom_bar(stat="summary",fun="mean", aes(fill=as.factor(date))) + 
  geom_point() +
  geom_hline(yintercept=750,linetype="dashed")+
  scale_y_continuous(breaks=c(0,500,750,1000,1500,2000,2500),labels=c(0,500,"A. brasilense",1000,1500,2000,2500)) +
  #annotate("text",x=100,y=750,label="A. brasilense (Van Deynze et. al 2018)") +
  ylab("Nanomoles of Ethylene/hr/OD600") +
  xlab("Isolate") +
  theme(axis.text.x = element_blank())

# Ethylene bar chart, samples done with old and new septa.
ggplot(data=multi, aes(x=`new-ID`, y=`nmol-eth/hr/OD`)) +
  geom_bar(stat="summary",fun="mean", aes(fill=as.factor(date))) + 
  geom_point() +
  geom_hline(yintercept=750,linetype="dashed")+
  scale_y_continuous(breaks=c(0,500,750,1000,1500,2000,2500),labels=c(0,500,"A. brasilense",1000,1500,2000,2500)) +
  #annotate("text",x=100,y=750,label="A. brasilense (Van Deynze et. al 2018)") +
  ylab("Nanomoles of Ethylene/hr/OD600") +
  xlab("Isolate") +
  theme(axis.text.x = element_text(angle=90, vjust=0.3))

# Ethylene bar chart, ordered by date. New septa only.
ggplot(data=data%>%filter(date>=20231208), aes(x=reorder(`new-ID`,`date`), y=`nmol-eth/hr/OD`)) +
  geom_bar(stat="summary",fun="mean", aes(fill=as.factor(date))) + 
  geom_point() +
  geom_hline(yintercept=750,linetype="dashed")+
  scale_y_continuous(breaks=c(0,500,750,1000,1500,2000,2500),labels=c(0,500,"A. brasilense",1000,1500,2000,2500)) +
  #annotate("text",x=100,y=750,label="A. brasilense (Van Deynze et. al 2018)") +
  ylab("Nanomoles of Ethylene/hr/OD600") +
  theme(axis.text.x = element_text(angle=90, vjust=0.3))

# Ethylene bar chart, Lactococcus and E. coli comparison.
ggplot(data=data%>%filter(grepl("BCW200241|Ecoli|BCW200232",ID))%>%filter(date=="20231210"), aes(x=`new-ID`, y=`nmol-eth/hr/OD`)) +
  geom_bar(stat="summary",fun="mean", aes(fill=date)) + 
  geom_point() +
  #geom_hline(yintercept=750,linetype="dashed")+
  #scale_y_continuous(breaks=c(0,500,750,1000,1500,2000,2500),labels=c(0,500,"A. brasilense",1000,1500,2000,2500)) +
  #annotate("text",x=100,y=750,label="A. brasilense (Van Deynze et. al 2018)") +
  ylab("Nanomoles of Ethylene/hr/OD600") +
  xlab("Isolate") +
  theme(axis.text.x = element_text(angle=90, vjust=0.3))
```

##### Extract Acetylene Peak Areas.
```{python ace}
toptop=pd.DataFrame()
for i in os.listdir("data/"):
  if os.path.isdir("data/"+i):
    path = "data/"+i
    for j in os.listdir(path):
      name = j.split("_",1)[1].replace("_rep1_MS.csv","").replace("_rep2_MS.csv","").replace("_rep3_MS.csv","").replace("_rep4_MS.csv","").replace("_MS_1.csv","").replace("_rep5_MS.csv","").replace("_MS.csv","")
      # At later dates, I stopped running neg for samples so I didn't say they were "pos". Need to add that label.
      if "pos" not in name and "neg" not in name:
        name = name+"_pos"
      data = pd.read_csv(path+"/"+j, header=3)
      data = data.iloc[:,1:24]
      # Note that these criteria are based on manual inspection of values, subject to change.
      data = data[data["RT"].between(4.7,5.4)]
      # If acetylene is present, it is the highest peak, so getting the highest peak within the RT range.
      data = data[data["Area"]==data["Area"].max()]
      data.insert(loc=0,column="ID",value=name)
      data.insert(loc=24,column="date",value=i)
      toptop = pd.concat([toptop,data], axis=0)
toptop.reset_index(drop=True,inplace=True)
finalace = toptop[~toptop["ID"].str.contains("blank")]
finalace = finalace[~finalace["ID"].str.contains("uninoc")]
finalace = finalace[~finalace["ID"].str.contains("neg")]
finalace = finalace[~finalace["ID"].str.contains("ppm")]
finalace = finalace[~finalace["ID"].str.contains("empty")]
finalace["new-ID"]=finalace["ID"].str.replace("_pos","_")+finalace["date"]
```

##### Plot acetylene values. Barcharts and mean acetylene vs. mean ethylene.
```{r plot-ace, fig.width=10}
ace=py$finalace
data=py$toptopnmol
ace$date=as.numeric(ace$date)

# Acetylene peak area, ordered by date.
ggplot(data=ace, aes(x=reorder(`new-ID`,`date`), y=Area)) +
  geom_bar(stat="summary",fun="mean", aes(fill=as.factor(date))) + 
  geom_point() +
  ylab("Acetylene Peak Area") +
  theme(axis.text.x = element_blank())

# Acetylene peak area, ordered by date.
ggplot(data=ace%>%filter(date>20240111), aes(x=reorder(`new-ID`,`date`), y=Area)) +
  geom_bar(stat="summary",fun="mean", aes(fill=as.factor(date))) + 
  geom_point() +
  ylab("Acetylene Peak Area") +
  theme(axis.text.x = element_text(angle=90, vjust=0.3))

# Combine mean acetylene and mean ethylene information.
mean_ace=ace%>%group_by(`new-ID`,date)%>%summarize(mean_ace_area=mean(Area))
mean_eth=data%>%group_by(`new-ID`,date)%>%summarize(mean_eth_area=mean(Area),mean_nmol_per_hr_OD=mean(`nmol-eth/hr/OD`))
test=merge(x=mean_eth,y=mean_ace,by=c("new-ID","date"))

# Mean acetylene vs. mean ethylene.
ggplot(data=test, aes(x=mean_ace_area,y=mean_eth_area,color=date)) +
  geom_point(size=4)
```

##### Get every vial's ethylene and acetylene peak areas.
```{python every-eth-ace}
# Acetylene.
toptop=pd.DataFrame()
for i in os.listdir("data/"):
  if os.path.isdir("data/"+i):
    path = "data/"+i
    for j in os.listdir(path):
      name = j
      # At later dates, I stopped running neg for samples so I didn't say they were "pos". Need to add that label.
      if "pos" not in name and "neg" not in name:
        name = name+"_pos"
      data = pd.read_csv(path+"/"+j, header=3)
      data = data.iloc[:,1:24]
      # Note that these criteria are based on manual inspection of values, subject to change.
      data = data[data["RT"].between(4.7,5.4)]
      # Some small peaks of non-ethylene mess with getting ethylene peak only.
      # If ethylene is present, it is the highest peak, so getting the highest peak within the RT range.
      data = data[data["Area"]==data["Area"].max()]
      data.insert(loc=0,column="ID",value=name)
      data.insert(loc=24,column="date",value=i)
      toptop = pd.concat([toptop,data], axis=0)
toptop.reset_index(drop=True,inplace=True)
finalace = toptop[~toptop["ID"].str.contains("blank")]
finalace = finalace[~finalace["ID"].str.contains("uninoc")]
finalace = finalace[~finalace["ID"].str.contains("neg")]
finalace = finalace[~finalace["ID"].str.contains("ppm")]
finalace = finalace[~finalace["ID"].str.contains("empty")]
finalace.set_index("ID",inplace=True)

# Ethylene.
top=pd.DataFrame()
for i in os.listdir("data/"):
  if os.path.isdir("data/"+i):
    path = "data/"+i
    for j in os.listdir(path):
      name = j
      # At later dates, I stopped running neg for samples so I didn't say they were "pos". Need to add that label.
      if "pos" not in name and "neg" not in name:
        name = name+"_pos"
      data = pd.read_csv(path+"/"+j, header=3)
      data = data.iloc[:,1:24]
      # Note that these criteria are based on manual inspection of values, subject to change.
      data = data[data["RT"].between(2.4,2.68)]
      # Some small peaks of non-ethylene mess with getting ethylene peak only.
      # If ethylene is present, it is the highest peak, so getting the highest peak within the RT range.
      data = data[data["Area"]==data["Area"].max()]
      data.insert(loc=0,column="ID",value=name)
      data.insert(loc=24,column="date",value=i)
      top = pd.concat([top,data], axis=0)
top.reset_index(drop=True,inplace=True)
finaleth = top[~top["ID"].str.contains("blank")]
finaleth = finaleth[~finaleth["ID"].str.contains("uninoc")]
finaleth = finaleth[~finaleth["ID"].str.contains("neg")]
finaleth = finaleth[~finaleth["ID"].str.contains("ppm")]
finaleth = finaleth[~finaleth["ID"].str.contains("empty")]
finaleth.set_index("ID",inplace=True)

# Combine acetylene and ethylene.
both=finaleth.join(finalace,lsuffix="_eth",rsuffix="_ace")
both.reset_index(inplace=True)
```

##### Plot acetylene vs. ethylene. For every vial.
```{r plot-every-eth-ace, fig.width=10}
data=py$both
data$date_ace=as.numeric(data$date_ace)
new_septa_data=data%>%filter(date_ace>=20231208)
old_septa_data=data%>%filter(date_ace<20231208)
# Removing outliers for modelling.
new_septa_data_filt=new_septa_data%>%filter(2.5E6<Area_ace & Area_ace<7.5E6)

# Construct linear models. Ethylene area as function of acetylene area.
old_model=lm(Area_eth ~ Area_ace, data=old_septa_data)
new_septa_model=lm(Area_eth ~ Area_ace, data=new_septa_data)
new_septa_filt_model=lm(Area_eth ~ Area_ace, data=new_septa_data_filt)

#All data.
ggplot(data=data, aes(x=Area_ace,y=Area_eth,color=as.factor(date_ace))) +
  geom_point(size=4) +
  scale_x_continuous(breaks=c(0,2.5E6,5E6,7.5E6,1E7,1.25E7,1.5E7,1.75E7),limits=c(0,1.75E7)) +
  scale_y_continuous(breaks=c(0,1E6,2E6,3E6,4E6,5E6),limits=c(0,5E6)) +
  xlab("Acetylene Peak Area") +
  ylab("Ethylene Peak Area")


# Old Septa. All available data.
ggplot(data=old_septa_data, aes(x=Area_ace,y=Area_eth,color=as.factor(date_ace))) +
  geom_point(size=4) +
  scale_x_continuous(breaks=c(0,2.5E6,5E6,7.5E6,1E7,1.25E7,1.5E7,1.75E7),limits=c(0,1.75E7)) +
  scale_y_continuous(breaks=c(0,1E6,2E6,3E6,4E6,5E6),limits=c(0,5E6)) +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("R^2 = ",signif(summary(old_model)$r.squared, 5),
                     "Intercept =",signif(old_model$coef[[1]],5 ),
                     " Slope =",signif(old_model$coef[[2]], 5),
                     " P =",signif(summary(old_model)$coef[2,4], 5)))

# New Septa. All available data.
ggplot(data=new_septa_data, aes(x=Area_ace,y=Area_eth,color=as.factor(date_ace))) +
  geom_point(size=4) +
  scale_x_continuous(breaks=c(0,2.5E6,5E6,7.5E6,1E7,1.25E7,1.5E7,1.75E7),limits=c(0,1.75E7)) +
  scale_y_continuous(breaks=c(0,1E6,2E6,3E6,4E6,5E6),limits=c(0,5E6)) +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("R^2 = ",signif(summary(new_septa_model)$r.squared, 5),
                     "Intercept =",signif(new_septa_model$coef[[1]],5 ),
                     " Slope =",signif(new_septa_model$coef[[2]], 5),
                     " P =",signif(summary(new_septa_model)$coef[2,4], 5))) +
  xlab("Acetylene Peak Area") +
  ylab("Ethylene Peak Area")

# New Septa. Excluding outliers.
ggplot(data=new_septa_data_filt, aes(x=Area_ace,y=Area_eth,color=as.factor(date_ace))) +
  geom_point(size=4) +
  scale_x_continuous(breaks=c(0,2.5E6,5E6,7.5E6,1E7,1.25E7,1.5E7,1.75E7),limits=c(0,1.75E7)) +
  scale_y_continuous(breaks=c(0,1E6,2E6,3E6,4E6,5E6),limits=c(0,5E6)) +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("R^2 = ",signif(summary(new_septa_filt_model)$r.squared, 5),
                     "Intercept =",signif(new_septa_filt_model$coef[[1]],5 ),
                     " Slope =",signif(new_septa_filt_model$coef[[2]], 5),
                     " P =",signif(summary(new_septa_filt_model)$coef[2,4], 5))) +
  xlab("Acetylene Peak Area") +
  ylab("Ethylene Peak Area")

# New Septa. Excluding two outliers. Zoomed in.
ggplot(data=new_septa_data_filt, aes(x=Area_ace,y=Area_eth,color=as.factor(date_ace))) +
  geom_point(size=4) +
  #scale_x_continuous(breaks=c(0,2.5E6,5E6,7.5E6,1E7,1.25E7,1.5E7,1.75E7),limits=c(0,1.75E7)) +
  #scale_y_continuous(breaks=c(0,1E6,2E6,3E6,4E6,5E6),limits=c(0,5E6)) +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("R^2 = ",signif(summary(new_septa_filt_model)$r.squared, 5),
                     "Intercept =",signif(new_septa_filt_model$coef[[1]],5 ),
                     " Slope =",signif(new_septa_filt_model$coef[[2]], 5),
                     " P =",signif(summary(new_septa_filt_model)$coef[2,4], 5))) +
  xlab("Acetylene Peak Area") +
  ylab("Ethylene Peak Area")
```

##### Ethylene standard curve visualization.
```{python std-curve}
toptop=pd.DataFrame()
for i in os.listdir("data/"):
  if os.path.isdir("data/"+i):
    path = "data/"+i
    top = pd.DataFrame()
    for j in os.listdir(path):
      name = j.split("_",1)[1].replace("_rep1_MS.csv","").replace("_rep2_MS.csv","").replace("_rep3_MS.csv","").replace("_rep4_MS.csv","").replace("_MS_1.csv","").replace("_rep5_MS.csv","").replace("_MS.csv","")
      # At later dates, I stopped running neg for samples so I didn't say they were "pos". Need to add that label.
      if "pos" not in name and "neg" not in name:
        name = name+"_pos"
      data = pd.read_csv(path+"/"+j, header=3)
      data = data.iloc[:,1:24]
      # Note that these criteria are based on manual inspection of values, subject to change.
      data = data[data["RT"].between(2.4,2.68)]
      # Some small peaks of non-ethylene mess with getting ethylene peak only.
      # If ethylene is present, it is the highest peak, so getting the highest peak within the RT range.
      data = data[data["Area"]==data["Area"].max()]
      data.insert(loc=0,column="ID",value=name)
      top = pd.concat([top,data], axis=0)
    # Blanking, and remove blanks from final dataframe.
    if "uninoc_pos" in top["ID"].to_list():
      blank = top[top["ID"]=="uninoc_pos"]["Area"].mean()
      top = top[top["ID"]!="uninoc_pos"]
      top["Area"] = top["Area"]-blank
      top.reset_index(drop=True,inplace=True)
      top.insert(loc=24,column="date",value=i)
      toptop = pd.concat([top,toptop], axis=0)
    else:
      blank = top[top["ID"]=="blank_pos"]["Area"].mean()
      top = top[top["ID"]!="blank_pos"]
      top["Area"] = top["Area"]-blank
      top.reset_index(drop=True,inplace=True)
      top.insert(loc=24,column="date",value=i)
      toptop = pd.concat([top,toptop], axis=0)
toptop.reset_index(drop=True,inplace=True)

ppmeth=toptop[toptop["ID"].str.contains("ppm")].reset_index(drop=True)
ppmeth["concentration"]=pd.to_numeric(ppmeth["ID"].str.replace("ppm_pos","").str.replace("ppm_N_pos",""))
# At STP, there are 669245.5nmol gas in 15mL of headspace. This is what we're assuming.
# To convert ppm to nmol of gas, simply take the proportion of the nmol total.
ppmeth["nmol"]= 669245.5*(ppmeth["concentration"]/1E6)
```


##### Plot std curves.
```{r plot-std-curve}
ppmeth=py$ppmeth
for (i in unique(ppmeth$date)){
  data=ppmeth%>%filter(date==i)
  model=lm(Area ~ nmol, data=data)
  plt = ggplot(data=data, aes(x=nmol,y=Area)) +
    geom_point(size=4) +
    stat_smooth(method = "lm", col="red") +
    scale_x_continuous(trans=scales::pseudo_log_trans(base = 10),breaks=c(0,1,10,100,1000,1E4,1E5)) +
    scale_y_continuous(trans=scales::pseudo_log_trans(base = 10),breaks=c(0,10,100,1000,1E4,1E5,1E6,1E7,1E8)) +
    labs(title = paste(i,"R^2 = ",signif(summary(model)$r.squared, 5),
                     "Intercept =",signif(model$coef[[1]],5 ),
                     " Slope =",signif(model$coef[[2]], 5),
                     " P =",signif(summary(model)$coef[2,4], 5))) +
    xlab("Ethylene Concentration (nmol)") +
    ylab("Ethylene Peak Area")
  show(plt)
}

ggplot(data=ppmeth%>%group_by(date), aes(x=nmol,y=Area,color=date))+
  geom_point(size=4)+
  scale_x_continuous(trans=scales::pseudo_log_trans(base = 10),breaks=c(0,1,10,100,1000,1E4,1E5)) +
  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10),breaks=c(0,10,100,1000,1E4,1E5,1E6,1E7,1E8)) +
  stat_smooth(method = "lm") +
  xlab("Ethylene Concentration (nmol)") +
  ylab("Ethylene Peak Area")
  
```